---
name: Truc-Ly
surname: Le-Huynh
#position: "my position"
#address: "Ho Chi Minh City, Vietnam"
#profilepic: "./img/me02.JPG"
www: lehuynh.rbind.io
email: "trucly.lehuynh@gmail.com"
github: le-huynh
linkedin: le-huynh-truc-ly
orcid: 0000-0002-5227-2185
date: "`r format(Sys.time(), '%B %Y')`"
aboutme: "A young researcher with expertise in microbiology and biostatistics. An avid R user for data analysis, visualization, and automation. Passionate about open science and the development of digital tools for research."
headcolor: 990000
docname:  CV
output:
  vitae::awesomecv:
    page_total: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)

library(here)
library(tidyverse)
library(vitae)
```

```{r data}
source(file = here("data/data.R"))
```

# Technical Skills
\footnotesize
* **Statistics** || Biostatistics, Frequentist and Bayesian Inference, Bayesian Modelling
* **Programming Languages** || R (advanced), Python, SAS
* **Markup Languages** || RMarkdown, LaTeX
* **DevOps Tools** || Git, GNU Make
* **Visualization** || ggplot2, Shiny
* **Laboratory** || 
    + Water quality analysis: Chlorophyll, COD, BOD, TSS, TN-TP, NO~2~-N, NO~3~-N, NH~4~-N, PO~4~-P, etc.
    + Molecular Biology: DNA extraction, PCR/qPCR, Agarose Gel Electrophoresis, etc.
    + Molecules analysis: High Performance Liquid Chromatography (HPLC), Fluorescence Spectroscopy, Spectrophotometry
* **Others** || Reproducible research, R package development

# Education

```{r edu}
edu %>%
        detailed_entries(
                with = degree,
                what = univ,
                why = detail,
                when = glue::glue("{startYear} - {endYear}",.na = ""),
                where = where
                )

```

# Research Experience

```{r exp}
exp %>%
        filter(include == "yes") %>%
        detailed_entries(
                with = title,
                what = unit,
                why = detail,
                when = glue::glue("{startMonth} {startYear} - {endMonth} {endYear}",.na = ""),
                where = where
                )

```

# Publications

1. Hoang, T. T. T., Ichinose, K., Morimoto, S., Furukawa, K., **Le-Huynh, T.-L.**, Kawakami, A. (2022). Measurement of anti‑suprabasin antibodies, multiple cytokines and chemokines as potential predictive biomarkers for neuropsychiatric systemic lupus erythematosus. *Clinical Immunology*, 237(March), 1–8. https://doi.org/10.1016/j.clim.2022.108980

2. Angalika, M. W. S., Suzuki, S., **Le‑Huynh, T.‑L.**, Itayama, T., Tanaka, W. (2022). Assessing nutrient budget of ungauged catchment using intermittent water quality markers. *Maejo International Journal of Energy and Environmental Communication*, 4(3), 1–10. https://doi.org/10.54279/mijeec.v4i3.247534

3. **Le‑Huynh, T.‑L.**, Iwami, N., Whangchai, N., Gutierrez, R., Shimizu, K., Itayama, T. (2022). Statistical analysis of the effects of environmental factors and fish species on class‑sorted phytoplankton composition in aquaculture ponds in northern Thailand. *Maejo International Journal of Energy and Environmental Communication*, 4(3), 32–38. https://doi.org/10.54279/mijeec.v4i3.247635

4. **Le‑Huynh, T.‑L.**, Itayama, T., Mitsunaga, K., Angalika, M., Suzuki, S. (2022). Application of hurdle Poisson model to predict the abundance of toxic cyanobacteria Microcystis in reservoirs. *Maejo International Journal of Energy and Environmental Communication*, 4(3), 47–51. https://doi.org/10.54279/mijeec.v4i3.247529

```{r paper, include=FALSE}
bibliography_entries("paper.bib") %>%
        arrange(issued)
```

# Selected Presentations

1. **Le-Huynh, T.-L.**, Iwami, N., Praphrute, R., Whangchai, N., Gutierrez, R., Shimizu, K., Itayama, T., Statistical analysis on phytoplankton population at hypertrophic ponds in northern Thailand [Oral presentation], *The 57th Annual Conference of Japan Society on Water Environment*, Ehime, Japan, March 2023.

2. **Le-Huynh, T.-L.**, Itayama, T., Mitsunaga, K., Angalika, M., Suzuki, S., Predict toxic cyanobacteria Microcystis in reservoirs by Bayesian hurdle Poisson model [Oral presentation], *1st Campus Asia Program International Symposium*, Nagasaki, Japan, February 2023.

3. **Le-Huynh, T.-L.**, Itayama, T., Mitsunaga, K., Using Bayesian hurdle Poisson model to predict cyanobacterial cell densities in Nagasaki reservoirs [Oral presentation], *The 56th Annual Conference of Japan Society on Water Environment*, Toyama, Japan, March 2022.

4. **Le-Huynh, T.-L.**, Mitsunaga, K., Itayama, T., A Bayesian model for predicting the growth of toxic Microcystis from air temperature and trophic state index [Oral presentation], *The 3rd International Conference on Renewable Energy, Sustainable Environmental and Agricultural Technologies*, Chiangmai, Thailand, December 2021.

5. **Le-Huynh, T.-L.**, Itayama, T., Nguyen, T. H. G., Xia, D., Shimizu, K., Iwami, N., Okano, K., Maseda, H., Praphrute, R., Ruangdet, K., Gutierrez, R., Whangchai, N., Influence of environmental factors on Microcystins degradation bacteria and toxigenic cyanobacteria bloom: a Bayesian approach [Poster presentation], *The NaToxAq Conference on Natural Toxins: Environmental Fate & Safe Water Supply*, Brno, Czech Republic, September 2020.

# Selected Awards

```{r awards}
awards %>%
        detailed_entries(
                with = area,
                what = where,
                why = detail,
                when = glue::glue("{startYear} - {endYear}",.na = ""),
                )

```






